---
title: "Viridis Demo"
output: html_document
---
# test
$f_{df}$

```{r include = FALSE}
library(viridis)
```
```{r}
fit2 <- lm(weight~height + I(height^2),data = women)
fit2
summary(fit2)

plot(women$height, women$weight,
     xlab = "height",
     ylab = "weight",
     main = "Regression2",
     col = c("purple","white"),
     pch = 17
     )
lines(women$height, women$weight,lty = 10)

```

The code below demonstrates two color palettes in the [viridis](https://github.com/sjmgarnier/viridis) package. Each plot displays a contour map of the Maunga Whau volcano in Auckland, New Zealand.


## Viridis colors

```{r}
image(volcano, col = viridis(200))
```

## Magma colors

```{r}
image(volcano, col = viridis(200, option = "A"))
```

## other test
ages1 <- runif(90,22,30)
ages2 <- runif(70,31,45 )
ages3 <- runif(40,46,60)
Ages <- c(ages1,ages2,ages3)

wages1 <- rnorm(90,mean=8000,sd=1000)
wages2 <- rnorm(70,mean=15000,sd=2000)
wages3 <- rnorm(40,mean=20000,sd=1500)
Wages <- c(wages1,wages2, wages3)

marker1 <- rep('22~30 years old',times = 90)
marker2 <- rep('31~45 years old',times = 70)
marker3 <- rep('46~60 years old', times = 40)
Groups <- c(marker1, marker2, marker3)

  
mydataframe <- data.frame(Groups, Ages, Wages,  stringsAsFactors = FALSE)
mydataframe
mydataframe$Groups <- factor(mydataframe$Groups)
